---
title: "Cait Harrigan, MSc."
format:
  html:
    toc: true
    toc_float: true
    toc-location: left
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')

```


```{r entries-setup, ehcho=F, warning=F, message=F}
source('formatter.R')

cv_entries <- cv_entries %>% subset(pdf_show == T) 
  

publications <- "files/harrigan.bib"
BibOptions(sorting = 'none')
refs <- rev(ReadBib(publications))
NoCite(refs)
```

<div id="cv_print_header">
<p id="cv-title">
Cait Harrigan, MSc.
</p>
cait.harrigan@mail.utoronto.ca | View this CV online at <a href="https://caitharrigan.ca/cv">caitharrigan.ca/cv</a>
</div>


::: {.column-margin}

<a id=print_button href="files/cv.pdf" class="btn btn-secondary icon-link">Print this CV</a>

:::

I am a graduate student at the University of Toronto supervised by [Quaid Morris](https://www.morrislab.ca/) and [Kieran Campbell](https://www.camlab.ca/). I'm a graduate researcher at the [Vector Institute](https://vectorinstitute.ai/) and Doctoral Fellow at the [UofT Data Sciences Institute](https://datasciences.utoronto.ca/). I did my undergraduate studies at the University of Toronto, in Computational Biology and Statistics. I use machine learning to understand cancer genomics by modelling the evolutionary constraints that underlie how mutation events occur in DNA. I'm passionate about open science, and promoting great mentorship in the sciences.




# Education

`r print_section(cv_entries, "education")`


# Professional Experience

`r print_section(cv_entries, "work")`

# Publications

<div class="grid cv-entry"><div class="g-col-1"><div class="cv-line"></div></div></div>

`r print_publications(refs)`


# Talks 

`r print_section(cv_entries, "talk_academic")`

# Posters 

`r print_section(cv_entries, "poster")`

# Service

<div class="grid cv-entry"><div class="g-col-1"><div class="cv-line"></div></div></div>

```{r, echo=F, warning=F, message=F}
# collate all service together
pr <- cv_entries %>% 
  filter(what == 'Peer review') %>%
  pull(where) %>%
  paste0(collapse = ', ')

pc <- cv_entries %>%
  filter(what == 'Conference program committee') %>%
  group_by(where) %>%
  summarise(description = paste0(year_begin, collapse=', ')) %>%
  mutate(description = paste0(where, ' (', description, ')')) %>%
  pull(description) %>%
  paste0(collapse = ', ')

pr <- c(
    '<div class= short-entry>',
    "<b>Peer review:</b> ",
    pr,
    '</div>'
)

pc <- c(
    '<div class= short-entry>',
    "<b>Conference program committee:</b> ", 
    pc,
    '</div>'
)

```

`r HTML(pr)`
`r HTML(pc)`

# Grants & Awards

`r print_section(cv_entries, "grants_and_awards")`


# Teaching

<em style="font-size:0.8rem">Unless otherwise noted, school is University of Toronto</em>

`r print_section(cv_entries, "teaching")`


# Event Organization

`r print_section(cv_entries, "event_org")`

# Progam Administration

`r print_section(cv_entries, "program_admin")`

