---
title: "Cait Harrigan, MSc."
format:
  html:
    toc: true
    toc_float: true
    toc-location: left
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')

```


```{r entries-setup, ehcho=F, warning=F, message=F}
source('formatter.R')

cv_entries <- cv_entries %>% subset(pdf_show == T)
  

publications <- "files/harrigan.bib"
BibOptions(sorting = 'none')
refs <- rev(ReadBib(publications))
NoCite(refs)
```

<div id=cv_print_header>
<center>
<p style="font-size: 15pt; font-weight:300; margin-bottom: 0.5em">
Cait Harrigan, MSc.
</p>

<p style="font-weight:400; margin-bottom: 0.5em">
cait.harrigan@mail.utoronto.ca \| View this CV online at [caitharrigan.ca/cv](https://caitharrigan.ca/cv)
</p>
</center>
</div>


<a id=print_button href="files/cv.pdf" class="btn btn-primary icon-link">Print this CV</a>

I am a graduate student at the University of Toronto supervised by [Quaid Morris](https://www.morrislab.ca/) and [Kieran Campbell](https://www.camlab.ca/), and a graduate researcher at the [Vector Institute](https://vectorinstitute.ai/). I did my undergraduate studies at the University of Toronto, in Computational Biology and Statistics. In my PhD work, I use machine learning to understand cancer genomics by modelling the evolutionary constraints that underlie how mutation events occur in DNA. I'm passionate about open science, and promoting great mentorship in the sciences.


## Memberships & Affiliations



`r print_section(cv_entries, "affiliation_and_membership")`


## Education

`r print_section(cv_entries, "education")`


## Work experience

`r print_section(cv_entries, "work")`

## Publications

`r print_publications(refs)`



## Talks 

`r print_section(cv_entries, "talk")`

## Posters 

`r print_section(cv_entries, "poster")`

## Grants & Awards

`r print_section(cv_entries, "grants_and_awards")`

## Service

```{r, echo=F, warning=F, message=F}
# collate all service together
pr <- cv_entries %>% 
  filter(what == 'Peer review') %>%
  pull(where) %>%
  paste0(collapse = ', ')

pc <- cv_entries %>%
  filter(what == 'Conference program committee') %>%
  group_by(where) %>%
  summarise(description = paste0(year_begin, collapse=', ')) %>%
  mutate(description = paste0(where, ' (', description, ')')) %>%
  pull(description) %>%
  paste0(collapse = ', ')

pr <- c(
    '<div class= short-entry>',
    # title
    '<span class="entry-title">',
    "Peer review:",
    '</span>',
    # contents
    '<span class="entry-body">',
    pr,
    '</span>',
    '</div>'
)

pc <- c(
    '<div class= short-entry>',
    # title
    '<span class="entry-title">',
    "Conference program committee: ",
    '</span>',
    # contents
    '<span class="entry-body">',
    pc,
    '</span>',
    '</div>'
)

```

`r HTML(pr)`
`r HTML(pc)`

## Teaching

<em style="font-size:0.8em">Unless otherwise noted, school is University of Toronto</em>

`r print_section(cv_entries, "teaching")`


## EventConference Organization

`r print_section(cv_entries, "event_org")`

## Progam Administration

`r print_section(cv_entries, "program_admin")`

