---
title: "Cait Harrigan, MSc."
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')

```


```{r entries-setup, ehcho=F, warning=F, message=F}
source('format_entries.R')
source('format_bib.R')

cv_entries <- cv_entries %>% subset(cv_short_show == T) 
  

publications <- "files/harrigan.bib"
BibOptions(sorting = 'none')
refs <- rev(ReadBib(publications))
NoCite(refs)
```

<div id="cv_print_header">
<p id="cv-title">
Cait Harrigan, MSc.
</p>
cait.harrigan@mail.utoronto.ca | View this CV online at <a href="https://caitharrigan.ca/cv">caitharrigan.ca/cv</a>
</div>


::: {.column-margin}

<a id=print_button href="files/cv.pdf" class="btn btn-secondary icon-link">Print this CV</a>

:::

I am a graduate student at the University of Toronto supervised by [Quaid Morris](https://www.morrislab.ca/) and [Kieran Campbell](https://www.camlab.ca/). I'm a graduate researcher at the [Vector Institute](https://vectorinstitute.ai/) and Doctoral Fellow at the [UofT Data Sciences Institute](https://datasciences.utoronto.ca/). I use machine learning to understand cancer genomics by modelling the evolutionary constraints that underlie how mutations occur in DNA. I'm passionate about open science, and promoting great mentorship in the sciences.



## Education

`r cv_entries %>% filter(type=='education') %>% print_section()`

## Research Experience

`r cv_entries %>% filter(type=='work') %>% print_section()`


## Publications

\* Indicates equal contribution

`r print_publications(refs)`

## Fellowships & Awards

`r cv_entries %>% filter(type=='award') %>% print_section()`


## Talks 

`r cv_entries %>% filter(type=='talk_academic') %>% print_section()`

## Research Mentorship

`r cv_entries %>% filter(type=='supervision') %>% print_section()`

<center>
Last updated: `r paste(lubridate::month(Sys.Date(), label=T), lubridate::year(Sys.Date()) )`
</center>
